The problem and promise of scale in animal social multilayer networks

### 2020-02-07 paper/manuscript.Rmd
little edits throughout

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes (i.e., recorded within 5 minutes of each other) were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
contexts.

@@

We altered the social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou<!-- TODO: REF?-->. Specifically, we
modified the spatial distance threshold required for group assignment using
`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
distances between 5-500 m. For example, at the finest social scale, only
individuals within 5 m of one another were considered in the same group, whereas
at the coarsest social scale, individuals within 500 m of one another were
considered in the same group.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology.
We aggregated the 10 m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation occurred
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. 10 m and 100 m represents fine-scale decision making
for caribou during foraging (Webber et al. unpublished data), while re-sampling at 500 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017).

@@

The integration of behavioural and ecological theory has shown the value of
considering the importance of scale to better understand and predict animal
social networks, including demography (Shizuka and Johnson 2019), evolutionary
and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
2017), and animal personality (Sih et al. 2017). While the number of studies
integrating social network theory into a broader array of behavioural and
ecological sub-disciplines is impressive, only recently has the role of animal
space use been considered in describing the causes and consequences of the
social environment in the context of (1) individual fitness and phenotypes
(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode
et al. 2011), and (3) habitat selection and space use (He et al. 2019). Here, we
explore how mutlilayer networks may apply to these emerging fields to contribute
to the development of social network theory and application.

## Individual fitness and phenotypes

>>>>

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, nodes represented individuals, intralayer edges represented
associations between individuals in a given habitat type and season, and
interlayer edges represented connections between the same individuals across
contexts.

@@

We altered the social scale based on visual (short distance) and auditory (long
distance) sensory modalities of caribou<!-- TODO: REF?-->. Specifically, we
modified the spatial distance threshold required for group assignment using
`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
distances between 5 - 500 m. For example, at the finest social scale, only
individuals within 5 m of one another were considered in the same group, whereas
at the coarsest social scale, individuals within 500 m of one another were
considered in the same group.

@@

To assess the influence of spatial scale on multilayer networks, we aggregated
our landcover raster at varying scales relevant to caribou ecology.
We aggregated the 10 m landcover raster using the R package `grainchanger`
[@Graham_2019] at five scales: 100 m, 250 m, 500 m, and 1000 m. Aggregation occurred
using a modal moving window method using a circular window corresponding to the
above scales [@Graham_2019a]. We assume 10 m and 100 m represents fine-scale decision making
for caribou during foraging (Webber et al. unpublished data), while re-sampling at 500 m and 1000 m
represents the scale at which caribou tend to select and avoid habitat
(Bastille-Rousseau et al. 2017).

@@

The integration of behavioural and ecological theory has shown the value of
considering the importance of scale to better understand and predict animal
social networks, including demography (Shizuka and Johnson 2019), evolutionary
and quantitative genetics (Fisher and McAdam 2017), disease ecology (Silk et al.
2017), and animal personality (Sih et al. 2017). While the number of studies
integrating social network theory into a broader array of behavioural and
ecological sub-disciplines is impressive, only recently has the role of animal
space use been considered in describing the causes and consequences of the
social environment in the context of (1) phenotypes and individual fitness
(Webber & Vander Wal 2018), (2)  movement ecology and collective movement (Bode
et al. 2011), and (3) habitat selection and space use (He et al. 2019). Here, we
explore how mutlilayer networks may apply to these emerging fields to contribute
to the development of social network theory and application.

## Phenotypes and Individual fitness
